\input{preamble}

\begin{document}
\section*{Assignment \#1: Setup Course Tools}

{\bf DUE:} Tuesday, 2016-09-06 at 08:30.

\begin{enumerate}

\item Login into \url{https://gitlab.oit.duke.edu} using your NetID using the Shibboleth login.  (This has to be done to give you access to the class GitLab group.)

\item Download and install \verb+git+ at \url{https://git-scm.com}.  We will be using Git Bash, \emph{not} a GUI client.

\item Setup an SSH key to seamlessly push/pull to/from your GitLab repositories: \url{http://docs.gitlab.com/ce/gitlab-basics/create-your-ssh-keys.html}  (Make sure that you use the OIT-hosted gitlab.oit.duke.edu server, not gitlab.com in the examples.)

\item Download and install \verb+python3+ at \url{https://www.continuum.io/downloads}.  Be sure to install Python 3.5, \emph{not} Python 2.7.

\item Download and install PyCharm at \url{https://www.jetbrains.com/pycharm/}.  You can get free access to the software through an academic license.  Note that if you already use another IDE for python projects (e.g., PyDev Eclipse), then you are free to continue to use that.

\item Never used git before?  Start with these resources:
\begin{itemize}
    \item \url{https://try.github.io/}
    \item \url{https://www.codecademy.com/learn/learn-git}
    \item \url{https://www.git-tower.com/learn/cheat-sheets/vcs-workflow}
    \item \url{http://gitimmersion.com/}
\end{itemize}

\item Familiar with git?  Give this a try: \url{http://learngitbranching.js.org/}

\item Having trouble?  Checkout the Duke Co-Lab, which hosts regular office hours and has an online Slack channel: \url{https://colab.duke.edu/}  (Dr. Palmeri is active on the Duke Co-Lab Slack channel.)

\item Demonstrate that you have git working on your local computer.
\begin{itemize}
\item Create a git repository on your local computer called ``bme590assignment01''.
\item Create a text file called ``hello\_world.txt'' that contains ``I deserve full credit on this assignment.'' in your repository.
\item Add and commit that file into your repository.
\item Create a repository on GitLab of the same name through your web browser.
\item Push your local repostiory to GitLab.
\item Add Dr. Palmeri (mlp6) and Brenton (bnk5) as ``Master'' collaborators.
\end{itemize}

\end{enumerate}

\end{document}
