\input{preamble}

\begin{document}
\section*{Assignment \#4: Heart Rate Monitor (v1.0.0)}

{\bf DUE:} Friday, 2016-10-21 at 17:00.

\begin{itemize}

\item Continue this assignment in your \verb+bme590assignment02+ repository,
    using the same ``good'' git practices along the way.

\item Make your code more robust to raised exceptions using \verb+try/except+
    statements.  Some key areas of your code to consider this infrastructure
        include:
\begin{itemize}
    \item Reading in binary data file
    \item Handling input file EOF condition
    \item Handling division by zero errors (if they may occur)
    \item Unexpected value errors
\end{itemize}

\item Expand the input functionality of your code to accommodate reading in a
    binary, HDF5, or Matlab data file.  Make sure to create unit tests for this
        functionality.
    
\item Add logging functionality to your code using the \verb+logging+ module.
\begin{itemize}
    \item Be sure to time stamp your log messages.
    \item Include DEBUG, INFO, and ERROR messages at locations you deem
        appropriate.  This does not need to be excessive, but appropriate for
        the level of modularity in your code (i.e., each major functional block
        can log some status).  
    \item Make sure that your heart rate estimates are included as INFO log
        entries whenever they are updated.
    \item Have your default log print at the DEBUG level.
\end{itemize}

\item Create a new git annotated tag of \verb+v1.0.0+ when you are done with the
    assignment.

\item Grading criteria:
\begin{itemize}
    \item Git usage (same as assignment 02 guidelines) [25\%]
    \item \verb+try/except+ implementation [25\%]
    \item Input file type accommodation [25\%]
    \item \verb+logging+ implementation [25\%]
\end{itemize}




\end{itemize}

\end{document}
