\input{preamble}

\begin{document}
\section*{Assignment \#01: Setup Course Tools \& Git Fundamentals}

{\bf DUE:} Tuesday, 2016-09-05 at 15:05.

\begin{enumerate}

\item Create an account on GitHub (\url{https://github./com}). 

\item Download and install \verb+git+ at \url{https://git-scm.com}.  We will be using Git Bash, \emph{not} a GUI client.

\item Setup an SSH key to seamlessly push/pull to/from your GitHub repositories: \url{https://help.github.com/articles/connecting-to-github-with-ssh/}

\item Download and install \verb+python3+ at \url{https://www.continuum.io/downloads}.  Be sure to install Python 3.6, \emph{not} Python 2.7.

\item Download and install PyCharm at \url{https://www.jetbrains.com/pycharm/}.  You can get free access to the software through an academic license using your Duke email address.  Note that if you already use another IDE for python projects (e.g., PyDev Eclipse), then you are free to continue to use that.

\item Never used git before?  Start with these resources:
\begin{itemize}
    \item \url{https://try.github.io/}
    \item \url{https://www.codecademy.com/learn/learn-git}
    \item \url{https://www.git-tower.com/learn/cheat-sheets/vcs-workflow}
    \item \url{http://gitimmersion.com/}
    \item \url{https://www.atlassian.com/git/tutorials/comparing-workflows#feature-branch-workflow}
\end{itemize}

\item Familiar with git (or just completed the exercises above)?  Give this a try: \url{http://learngitbranching.js.org/}

\item Having trouble?  We'll be reviewing some of these tools in lecture on Thursday.  Also checkout the Duke Co-Lab, which hosts regular office hours and has an online Slack channel: \url{https://colab.duke.edu/}

\item Learning Objectives:
\begin{itemize}
	\item Create a git repository on your local computer. 
	\item Create a local file, then add and commit it to your local repository.
	\item Edit your local file, adding and committing those edits.
	\item Create a remote repository on GitHub that has the same name as your local repository.
	\item Add the remote repository (origin) URL to your local repository.
	\item Push your local repostiory to GitHub.
	\item Create a local branch, create/add/commit a new file.
	\item Merge new local branch commit(s) into local master.
	\item Push updated master branch to GitHub.
\end{itemize}

\end{enumerate}

\end{document}
